A Survey of Wearable Device Risk Perceptions

### 2015-01-06 wearables_survey.tex
changed transitions in methodology intro

\section{Methodology}
Our survey consisted of multiple sections. In one section, we presented participants with scenarios surrounding a wearable device and asked them to rate their level of concern if each scenario were to happen. In another section of the survey, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones). In another section of the survey, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies. Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.

>>>>

\section{Methodology}
Our survey consisted of multiple sections. In one section, we presented participants with scenarios surrounding a wearable device and asked them to rate their level of concern if each scenario were to happen. Next, we asked participants about similar scenarios, substituting smartphones for the wearable device in order to see whether participants' familiarity with the devices impacted their risk perceptions (i.e., we expected all participants to be much more familiar with smartphones). Following those questions, we asked participants to compare the risks and benefits of wearable technologies with better understood technologies. Finally, we collected demographic information, which included a privacy concern scale, and whether participants owned any wearable devices.
